---
title: "CASE STUDY TITLE"
author: "YOUR NAME"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 15

---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```


## Background

Finding good data takes time, and can take longer than the time to tidy your data. This task could easily take 3-6 hours to find the data you need for your semester project. After you find good data sources make sure to complete the remaining tasks.

## Reading
Vectors
  Atomic Vectors - homogeneous
  lists - heterogeneous


```{r practice}
typeof(letters)
#> [1] "character"
typeof(1:10)
#> [1] "integer"

x <- list("a", "b", 1:10)
length(x)
#> [1] 3

1:10 %% 3 == 0
#>  [1] FALSE FALSE  TRUE FALSE FALSE  TRUE FALSE FALSE  TRUE FALSE

c(TRUE, TRUE, FALSE, NA)
#> [1]  TRUE  TRUE FALSE    NA

typeof(1)
#> [1] "double"
typeof(1L)
#> [1] "integer"
1.5L
#> [1] 1.5

NA            # logical
#> [1] NA
NA_integer_   # integer
#> [1] NA
NA_real_      # double
#> [1] NA
NA_character_ # character
#> [1] NA

x <- sample(20, 100, replace = TRUE)
y <- x > 10
sum(y)  # how many are greater than 10?
#> [1] 38
mean(y) # what proportion are greater than 10?
#> [1] 0.38
```
"Step 1: Learn about the elephant Unless the data is something I’ve analyzed a lot before, I usually feel like the blind men and the elephant."
If you don't understand every part of your data, you will never ever be able to fully unlock its potential. 


## Data Visualization

```{r plot_data}
# Use this R-Chunk to plot & visualize your data!
getwd()
dat1 <- read_csv("trumptweets.csv") %>% 
  select(date:favorites) %>% 
  group_by(date) %>% 
  filter(date > "2018-01-01 00:00:00" && date < "2018-02-01 00:00:00")
View(dat1)

dat1 %>% 
  ggplot(aes(x = date)) + 
  geom_point(aes(y = retweets / 10000), color = "darkred") +
  geom_point(aes(y = favorites / 10000), color = "blue")+
  theme_bw() +
  labs(title = "Trump Tweet Stats", y = "Amount (10,000)", 
       x = "Date", color = "Reaction")


dat2 <- read.table("newsArticlesWithLabels.tsv", sep = "\t", header = TRUE) %>% as_tibble()
View(dat2)
dat3 <- read_csv("fake.csv") %>% as_tibble()
View(dat3)
```

## Conclusions
