---
title: "Case Study 2: Wealth and Life Expectancy (Gapminder)"
author: "Christopher Wilson"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}
# Use this R-Chunk to load all your libraries!
#install.packages("tidyverse") # run this line once in console to get package
library(tidyverse)

```

```{r load_data}
# Use this R-Chunk to import all your datasets!
library(gapminder)

```

## Background

Hans Rosling is one of the most popular data scientists on the web. His original TED talk was very popular among my friends when it came out. We are going to create some graphics using his formatted data as our weekly case study. Note that we need to remove Kuwait from the data (discussion on this)

## Data Wrangling

```{r tidy_data}
# Use this R-Chunk to clean & wrangle your data!
# "...we need to remove Kuwait from the data..."
dat <- subset(gapminder, country != "Kuwait")
View(dat)

```

## Data Visualization

```{r plot_data_1, fig.width=15}
# Use this R-Chunk to plot & visualize your data!
dat %>%
  ggplot(aes(lifeExp, gdpPercap)) +
  geom_point(aes(size = pop / 100000, color = continent)) +
  facet_wrap(~ year, nrow = 1) + 
  labs(colour = "Continent", size = "Population (100k)") + 
  xlab("Life Expectancy") + ylab("GDP per capita") + 
  theme_bw() + 
  theme(axis.text = element_text(size = 6), strip.text.x = element_text(size = 7)) +
  scale_y_continuous(trans = "sqrt")

ggsave("cs2.1.png", plot = last_plot(), width = 15, units = c("in"))

```

```{r plot_data_2, fig.width=15}
# Use this R-Chunk to plot & visualize your data!
avg <- dat %>%
  group_by(year, continent) %>%
  mutate(gdpPercap = weighted.mean(gdpPercap, pop / 100000))

dat %>%
  ggplot(aes(year, gdpPercap, color = continent)) +
  geom_line(aes(group = country)) + 
  geom_point(aes(size = pop / 100000, color = continent)) +
  geom_line(data = avg, color = "black") +
  geom_point(data = avg, aes(size = pop / 100000), color = "black") +
  facet_wrap(~ continent, nrow = 1) +
  labs(colour = "Continent", size = "Population (100k)") + 
  xlab("Year") + ylab("GDP per capita") + 
  theme_bw() + 
  theme(axis.text = element_text(size = 6), strip.text.x = element_text(size = 7))

ggsave("cs2.2.png", plot = last_plot(), width = 15, units = c("in"))

```

## Conclusions

Taking the average of something can really be innacurate Sure, the average represented the continent's GDP, but each country had a tremendous amount of variation. The GDP in the americas was vastly different, with the US and Canada as strong outliers. We can't use the average as a representation of the whole!