---
title: "CASE STUDY TITLE"
author: "YOUR NAME"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_height: 6
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}
# Use this R-Chunk to load all your libraries!
#install.packages("tidyverse") # run this line once in console to get package
library(tidyverse)

```

```{r load_data}
# Use this R-Chunk to import all your datasets!
setwd("/Users/CritterWilson/Documents/BYU-I/Software Engineering/MATH335/M335_WI20_Wilson_Chri/Case_Study_03/Class_Task_05")
dat <- read_csv("share-food-miles-by-method.csv", na = c("", "na"))
mort <- ourworldindata::child_mortality

```

## Background

_Place Task Background Here_

## Data Wrangling

```{r tidy_data}
# Use this R-Chunk to clean & wrangle your data!
View(dat)
mort <- mort %>%
  select(year, country, population, child_mort) %>% 
  filter(year > 1925, country == "United States" | country == "Italy")
View(mort)
```
## Data Visualization

```{r plot_data}
# Use this R-Chunk to plot & visualize your data!
dat %>%
  ggplot(aes(`Entity`, `Share of food miles by transport method (%)`, 
             label = `Share of food miles by transport method (%)`, fill = Entity)) +
  geom_col(stat = "identity") +
  coord_flip() +
  geom_label() +
  scale_y_continuous(breaks=(seq(0, 60, by = 10))) +
  scale_y_sqrt() +
  theme_bw ()

mort %>% 
  ggplot(aes(year, child_mort, color = country)) +
  geom_line() +
  labs(title = "Child Mortality Rates in the United States & Italy",
      x = "Year", y = "Child Mortality Rater\nper 1000 Children Born", 
      color = "Country") +
  theme_bw()
  

```

## Conclusions
My first chart was very hard to replicate. I struggled to include the right labels on the bar, but I did what I could with the time I had. For my mortality chart, my wife served in italy and I was interested to compare a historic nation like italy with a very young nation like the US. I was surprised to see how the US struggled a LOT in 1925 compared to italy but have since surpassed them. 
