---
title: "Interacting With Time"
author: "Christopher Wilson"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 15
    fig_align: 'center'
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}
# Use this R-Chunk to load all your libraries!
#install.packages("tidyverse") # run this line once in console to get package
pacman::p_load(tidyverse, lubridate, dygraphs, DT, timetk, tidyquant)
```

```{r load_data}
# Use this R-Chunk to import all your datasets!
tickers_today <- c("CXW", "F", "GM", "JCP", "KR", "WDC", "NKE","T", "WDAY", "WFC", "WMT")
present <- today()
past <- present - years(5)

dat <- tq_get(tickers_today, get = "stock.prices", from = past, to = present)

```

## Background

_Place Task Background Here_

## Data Wrangling

```{r tidy_data}
# Use this R-Chunk to clean & wrangle your data!

```

## Data Visualization

```{r plot_data}
# Use this R-Chunk to plot & visualize your data!
dat %>% 
  select(date, close, symbol) %>% 
  pivot_wider(names_from = symbol, values_from = close) %>% 
  tk_xts() %>% 
  dygraph() %>% 
  dyRangeSelector(height = 20)

dat %>% 
  ggplot(aes(x = date, y = volume / 10000, color = symbol, fill = symbol)) +
  geom_line() +
  facet_wrap(~symbol, ncol = 2) +
  scale_y_sqrt() +
  theme_bw() +
  labs(x = "Date", y = "Volume / 10,000", title = "Volume per Stock",
       color = "Stock")

  
```

## Conclusions
In my visualizations, I chose to use the closing value because I like to know the finishing values of my stocks at the end of the day. In my interactive graph, I am using the range scaler at the bottom to make sure that we can get both general and precise values. 

I am seeing that WDAY did very well overtime but has crashed (along with everyone else) this week. In volumne, however, I am seeing the best values from F and T. 

